%-------------------------
% Resume in Latex
% Author : Nathan Pannell
% Template Author : Aras Güngöre
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

%---------- FONT OPTIONS ----------
% sans-serif
\usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{0pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{3pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{5pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
      \small#3 & \small #4 \\
      \small#5 & \small #6 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{5pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Nathan Pannell} \\ \vspace{10pt}
    \small
    \hspace{.5pt} \href{tel:16042022018}{604 202 2018}
    $|$
    \hspace{.5pt} \href{mailto:contact@nathanpannell.com}{contact@nathanpannell.com}
    $|$
    \hspace{.5pt} \href{https://www.linkedin.com/in/nathanpannell}{\textbf{linkedin}.com/in/nathanpannell}
    $|$
    \hspace{.5pt} \href{https://github.com/nathanpannell}{\textbf{github}.com/nathanpannell}
    $|$
    \hspace{.5pt} \href{https://nathanpannell.com}{nathanpannell.com}
\end{center}

%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeEducationHeading
      {\textbf{University of Victoria} $|$ Victoria, BC}{Sept 2021 \textbf{--} Present}
      {B.Sc. (Computer Science with Business Minor; Expected graduation - May 2025)}{}
      {\textbf{--} Award of Excellence Scholarship}{Jun 2021}
  \resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Programming Languages:}{ Python, JavaScript, PostgreSQL, Java, HTML, CSS} \\ \vspace{3pt}
        \textbf{Development Tools:}{ Git, Linux, REST APIs, Visual Studio Code, React, Tailwind } \\ \vspace{3pt}
        \textbf{Office 365 Tools:}{ Power BI, Power Automate, Azure DevOps, Excel, Outlook } \\ \vspace{3pt}
    }}
  \resumeSubHeadingListEnd
  
%----------- WORK EXPERIENCE -----------

\section{Work Experience}
  \vspace{-3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Global Talent Technology Co-Op}{May 2024 \textbf{--} Present}
      {Teck Resources Ltd, Vancouver, BC | International Mining \& Exploration}{Co-Op}
        \resumeItemListStart
            \resumeItem{Supported recruiters worldwide with a \textbf{suite of 18 applications} to streamline processes and increase efficiency.}
            \resumeItem{Built a custom chat bot to automate support issue submission and resolution, \textbf{reducing ticket volumes by 20\%}.}
            \resumeItem{Migrated VM-based automation script to \textbf{Azure Function Apps} to improve reliability and up-time.}
        \resumeItemListEnd

    \resumeSubheading
      {Automation Developer Co-Op}{May \textbf{--} Aug 2023}
      {AMJ Campbell, Delta, BC | Nation-wide Logistics}{Co-Op}
        \resumeItemListStart
            \resumeItem{Created automations with REST APIs, VBA, and Excel to \textbf{improve efficiency by 10\%} within the accounting department.}
            \resumeItem{Streamlined generation of billings and reports for accounts such as Wayfair and Crate \& Barrel.}
            \resumeItem{Handled \textbf{accounts payable} and \textbf{payroll} management for Vancouver, Victoria, and Kelowna during a staff member's leave.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%----------- LEADERSHIP EXPERIENCE -----------

\section{Leadership Experience}
  \vspace{-3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Simulation Project Lead}{Jan 2024 \textbf{--} Present}
      {UVic AI, Victoria, BC | Student-run Educational Club}{Volunteer}
        \resumeItemListStart
            \resumeItem{Led AI-driven wildfire simulation, presented in Kingston, Ontario at the \textbf{Canadian Undergraduate Conference on AI}.}
            \resumeItem{\textbf{Hosted university-wide hackathon} with a custom submission and visualization pipeline, with sponsorship from IEEE.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
        {\textbf{Wildfire Simulation with AI Agents} $|$ \emph{\href{https://github.com/uvicaiclub/WildfireManagementRL}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Created a cellular automata model of wildfire spread integrated with the \textbf{OpenAI Gymnasium API} for an AI Conference.}
            \resumeItem{Identified a novel wildfire simulation approach, including heuristic AI firefighter agents within the simulation itself.}
            \resumeItem{Collaborated with Reinforcement Learning and Domain Expert teams to ensure interoperability and accuracy.}
          \resumeItemListEnd
    
      \resumeProjectHeading
        {\textbf{Interactive Hackathon Visualizer} $|$ \emph{\href{https://github.com/NathanPannell/uttt-visual}{\color{blue}GitHub}} }{}
          \resumeItemListStart
            \resumeItem{Developed a real-time visualization tool with \textbf{React} for presenting submissions at the UVic AI Club 2024 Hackathon.}
            \resumeItem{Designed a \textbf{base-81 encoding scheme} to effectively represent temporal-positional data as strings.}
            \resumeItem{Implemented a web interface to support hackathon participants in testing and debugging their AI agents.}
          \resumeItemListEnd
		  
      \resumeProjectHeading
        {\textbf{Virtual Rubik's Cube} $|$ \emph{\href{https://github.com/NathanPannell/virtual-cube}{\color{blue}GitHub}} $|$
        \emph{\href{https://nathanpannell.github.io/virtual-cube/cube.html}{\color{blue}Website}}}{}
          \resumeItemListStart
            \resumeItem{Built an interactive 3D Rubik's cube with JavaScript and CSS rotations, responsive on mobile and desktop.}
          \resumeItemListEnd
		  
    \resumeSubHeadingListEnd

%----------- REFERENCES -----------

% \section{References}
%   \vspace{2pt}
%   \resumeSubHeadingListStart
%     \item{References available upon request.}
%   \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}